{$\ch_2(\tf)$ Optimality Conditions for a Finite-time Horizon\thanksref{mytitlenote}}

### 2019-04-17 FH Optimality Conditions Paper.tex
Formating of main proof
added footnote

%FH model reduction
\section{$\ch_2(\tf)$ Optimal Model Reduction on a Finite Horizon}  \label{sec:main} 
%If we are interested  in the behavior of a system only in a finite time interval (or access to a numerical simulation only on a finite time interval), we can obtain better reduced models by defining the measure of approximation quality over the interval of interest, instead of  focussing on the infinite time horizon. 
%
{\color{red}
In this section, we discuss the main result of the paper i.e. the $\ch_2(\tf)$ local optimality conditions, their proof, and the importance of such conditions for model reduction of large-scale dynamical systems.}

@@

\emph{{Proof of Theorem \ref{mh2opt}.}}

>>>>

%FH model reduction
\section{$\ch_2(\tf)$ Optimal Model Reduction on a Finite Horizon}  \label{sec:main} 
%If we are interested  in the behavior of a system only in a finite time interval (or access to a numerical simulation only on a finite time interval), we can obtain better reduced models by defining the measure of approximation quality over the interval of interest, instead of  focussing on the infinite time horizon. 
%
{\color{red}
In this section, we discuss the main result of the paper i.e. the $\ch_2(\tf)$ \footnote{Even though we are on the time domain we will still use the $\ch_2(\tf)$ notation. Since the time domain and frequency domain functions are equivalent,  this notation is appropriate. Furthermore, since the infinite horizon, and finite horizon case appear to be connected, the notation $\mathcal{H}_2(t_f)$ illustrates this connection. \cite{RedK17,GoyR17} use similar notation.} local optimality conditions, their proof, and the importance of such conditions for model reduction of large-scale dynamical systems.}

@@

\textbf{{PROOF OF THEOREM \ref{mh2opt}.}}
